---
title: "Volunteer Survey 2015"
author: "Hunter Ratliff"
date: "January 4, 2016"
output: html_document
runtime: shiny
---

<!--- SET the Globals --->
```{r global_options, include=FALSE}
require(knitr)
## Define global settings for chunk output
knitr::opts_chunk$set(fig.width=9, fig.height=9, fig.align='center',      
                      fig.path='Figures/',                        # Sets output for figures
                      echo=FALSE, warning=FALSE, message=FALSE)        # Silences most chunk outputs

## Load required packages
# Make a vector of the names of packages we plan to use
packs <- c("magrittr", "dplyr", "reshape2", "ggplot2", "lubridate", "RColorBrewer",
           "stringr", "ggthemes", "scales", "gridExtra", "googlesheets", "plotly")

# Apply the require fxn to each package in list
sapply(packs, require, character.only=TRUE)
rm(packs)

## The 'source' function runs the R script of the provided path 
# See code:         https://github.com/HunterRatliff1/Citations
source("~/Github/Citations/Citation Function.R")
rm(citation.htr, citation.date)

## Theme object for ggplots
source("~/Github/utexas/diveristy/theme_UT.R")
```

```{r}
# df.quan <- gs_title("Volunteer Surveys") %>% 
#   gs_read_csv("2015_Quan")

df.2015 <- gs_title("Volunteer Surveys") %>% 
  gs_read_csv("2015") %>%
  mutate(Hours.PerMonth = factor(Hours.PerMonth,
                                 levels=c("0-5 hrs", "5-10 hrs", "10-20 hrs", 
                                          "20-40 hrs", "40-60 hrs", 
                                          "60-100 hrs", "100+ hrs"),
                                  ordered = T))
  unique(df.2015$Hours.PerMonth)
  
df <- df.2015 %>% select(Response.ID, Issues.Lead:Issues.Staff) %>%
  melt(id.vars = "Response.ID", na.rm = T, variable.name = "IssueWith") %>% 
  mutate(IssueWith = gsub("Issues.", "", IssueWith)) %>% 
  # Add response as factor
  left_join(as_data_frame(list(value=c(1:3), Response=c("Never", "Sometimes", "Often")))) %>%
  mutate(Response = factor(Response, levels=c("Never", "Sometimes", "Often"), ordered = T)) %>%
  
  left_join(select(df.2015, Response.ID, Hours.PerMonth, Plan.To.Continue)) %>%
  tbl_df()  
```

This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r, echo=FALSE}


inputPanel(
  selectInput("match_var", "Color By:", 
                  choices = c("Monthly Hours", "Plan to continue volunteering"))
)
#   selectInput("n_breaks", label = "Number of bins:",
#               choices = c(10, 20, 35, 50), selected = 20),
#   
#   sliderInput("bw_adjust", label = "Bandwidth adjustment:",
#               min = 0.2, max = 2, value = 1, step = 0.2)

datasetInput <- reactive({
    switch(input$match_var,
           "Monthly Hours" = df$Hours.PerMonth,
           "Plan to continue volunteering" = pressure)
  
  
renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})

# inputPanel(
#   selectInput("n_breaks", label = "Number of bins:",
#               choices = c(10, 20, 35, 50), selected = 20),
#   
#   sliderInput("bw_adjust", label = "Bandwidth adjustment:",
#               min = 0.2, max = 2, value = 1, step = 0.2)
# )
# 
# renderPlot({
#   hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
#        xlab = "Duration (minutes)", main = "Geyser eruption duration")
#   
#   dens <- density(faithful$eruptions, adjust = input$bw_adjust)
#   lines(dens, col = "blue")
# })
```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package="shiny"),
  options=list(
    width="100%", height=550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



